CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

df_schema2 = df_schema[,data.frame(ENSEMBL = Gene,
									OR1 = `OR (Class I)`,
									OR2 = `OR (Class II)`,
									P.value = `P meta`)]
```

@@

```{r plot.enrich.Dx_Sex, fig.width=9}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx_Sex, module, 8) + ggtitle(module) 
	}) 
plot_grid(plotlist = figList, ncol=1)
```

>>>>

df_schema2 = df_schema[,data.frame(ENSEMBL = Gene,
									OR1 = `OR (Class I)`,
									OR2 = `OR (Class II)`,
									P.value = `P meta`)]

df_schema2$chisq = qchisq(df_schema2$P.value, 1, lower.tail=FALSE)
df_schema2 = df_schema2[!is.na(df_schema2$P.value),]

rownames(df_schema2) = df_schema2$ENSEMBL
```

@@

```{r plot.enrich.Dx_Sex, fig.width=7, fig.height=12}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx_Sex, module, 8) + ggtitle(module) 
	}) 
plot_grid(plotlist = figList, ncol=1)
```
